Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-06-14 paper/ms.tex
last JEMR check

A different approach to infer the typical mass of halos hosting
LAEs is based on the spatial clustering information. 
This approach uses the fact
that in CDM cosmologies the spatial clustering of galaxies on large
scales is entirely dictated by the halo distribution
\citep{Colberg00}, which in turn has a strong dependence on halo
mass. 
Using measurements of the angular correlation function of LAEs,
observers have put constraints on the typical mass and occupation
fraction of the putative halos hosting these galaxies
\citep{Hayashino2004,Gawiser07,Nilsson2007,Ouchi2010,Bielby16}. 
In these studies the observations are done on fields of $\sim 1$ deg$^{2}$ and
the conclusions derived on the halo host mass do not elaborate deeply on the
uncertainty resulting from the cosmic variance on these fields. 
For instance, \citet{Guaita2010} attempted to analytically 
estimate the uncertainty from cosmic variance 
following \citet{Somerville2004} and \citet{Peebles1980}. 
Their prescription assumed that the correlation function can be
represented by a power-law
$\psi\left(r\right)=\left(r_{0}/r\right)^{\gamma}$. 
Their estimation of cosmic variance strongly depends on $r_{0}$ and
$\gamma$.  
However, $\gamma$ is only poorly constrained with current
observations which in turns indicates that their cosmic variance
estimation could not be precise.

@@

We chose this simulation based on three requirements. 
First, the simulation has cosmological parameters consistent
with the most recent constraints from Cosmic Microwave Background
experiments and provide public acces to the data.
Second, the halo mass function from the simulation is robust
down to  $10^{10}$\hMsun, which is the lower halo mass bound suggested
by previous observational 
studies\citep{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16}. 
Third, the total volume of the simulation is at least 10 times
larger the equivalent volume of a single LAE observation field.
These conditions are met as we describe below.

>>>>

A different approach to infer the typical mass of halos hosting
LAEs is based on the spatial clustering information. 
This approach uses the fact
that in CDM cosmologies the spatial clustering of galaxies on large
scales is entirely dictated by the halo distribution
\citep{Colberg00}, which in turn has a strong dependence on halo
mass. 
Using measurements of the angular correlation function of LAEs,
observers have put constraints on the typical mass and occupation
fraction of the putative halos hosting these galaxies
\citep{Hayashino2004,Gawiser07,Nilsson2007,Ouchi2010,Bielby16}. 
In these studies the observations are done on fields of $\sim 1$ deg$^{2}$ and
the conclusions derived on the halo host mass do not elaborate deeply on the
uncertainty resulting from the cosmic variance on these fields. 
For instance, \citet{Guaita2010} attempted to analytically 
estimate the uncertainty from cosmic variance 
following \citet{Somerville2004} and \citet{Peebles1980}. 
Their prescription assumed that the correlation function can be
represented by a power-law
$\xi\left(r\right)=\left(r_{0}/r\right)^{\gamma}$. 
Their estimation of cosmic variance strongly depends on $r_{0}$ and
$\gamma$.  
However, $\gamma$ is only poorly constrained with current
observations which in turns indicates that their cosmic variance
estimation could not be precise.

@@

We chose this simulation based on three requirements. 
First, the simulation has cosmological parameters consistent
with the most recent constraints from Cosmic Microwave Background
experiments and provide public acces to the data.
Second, the halo mass function from the simulation is robust
down to  $10^{10}$\hMsun, which is the lower halo mass bound suggested
by previous observational 
studies \citep{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16}. 
Third, the total volume of the simulation is at least 10 times
larger than the equivalent volume of a single LAE observational field.
These conditions are met as we describe below.
